Plan for $\bar{\nu}_\mu$ CC inclusive cross section measurement

### 2016-12-14 NumubarAnalysisPlanDec2016/numubar_analysis_plan.tex
finished document

\subsection{Constraint on Wrong Sign Contamination}

>>>>

\subsection{Constraint on Wrong Sign Contamination}
The wrong sign component could be constrained by looking for distributions which have different shapes for $\nu_\mu$ and $\bar{\nu}_\mu$ and fitting the data distribution to the two templates. Two distributions are found to have different shapes, namely the CCQE muon angle and the distance between the reco neutrino interaction vertex and the starting point of the subleading reco Kalman track of 2 track CCQE events.

\section{Timeline}
Determining datasets to use and event selection only need some fine-tuning and therefore not much more time is needed for these two items. As for background estimation, flux predictions, unfolding and systematic uncertainties, although for $\bar{\nu}_\mu$ CC numbers will be different from those for $\nu_\mu$ CC, the machineries leading to the numbers are very much the same. If all the machineries are developed, the time needed will be that for generating customized Monte Carlo samples and rerun the scripts. Given the size of MC samples I had generated before for nuclear model study, 4 weeks is my current estimate. Lastly, the only item that does not exist in the $\nu_\mu$ CC measurement is the wrong sign constraint. Four weeks is my estimate for this item.\\
In summary,
\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|}
    \hline
    items & time needed \\
    \hline
    determining datasets, event selection & 2 weeks if needed \\
    \begin{scriptsize}background estimation, flux predictions, unfolding, systematic uncertainties\end{scriptsize} & follow $\nu_\mu$ CC, 4 weeks\\
    wrong sign constraint & 4 weeks\\
    \hline
  \end{tabular}
\end{table}
